---
title: "Publishing Markdown"
subtitle: "A short tutorial for Class 3EE"  
author: ""
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

# Recap

By now, you would have:

* Learned what Markdown is and what it's used for;

* Learned how to write Markdown, the front matter and the syntax;

* Written your own Markdown document using text from your newspaper articles; and,

* Saved your Markdown document waiting for publication online.

---

class: center, middle

## Now you are ready to publish your Markdown document online.

---

# Things you need:

* A computer that can get on the internet;

* The Markdown document/s that you have already converted into Markdown;

* Permission from your parents and a little bit of help in doing all the online stuff;

---

# Overview of publishing a Markdown document online

* Markdown documents on their own are just lines of text and code that include information on what the document would and should look like when published

* The code and syntax that you have placed in your Markdown document needs to be read and interpreted by a computer who understands Markdown language. This is called `parsing` of the Markdown document and the computer that knows how to read and interpret Markdown is called a `parser`

* After `parsing`, the computer will then convert your Markdown document into another format that is ready for online publication. This format is called `HTML` format

* Once converted, your document is then published online ready to be viewed by yourself and others on the internet

---

# Typical workflow of publishing a Markdown document online

```{r workflow1, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 14}
DiagrammeR::mermaid("
  graph LR
    X(START) --> A[<center>1.<br/>Write<br/>Markdown<br/>document</center>] 
    A        --> B[<center>2.<br/>Send Markdown<br/>document to<br/>a Markdown<br/>interpreter/parser</center>]
    B        --> C[<center>3.<br/>Markdown<br/>document is<br/>converted<br/>to HTML</center>]
    C        --> D[<center>4.<br/>HTML is<br/>published<br/>online</center>]
    D        --> Y(END)
  ", 
  height = 200)
```

---

# Our workflow for publishing Markdown to online newspaper

```{r workflow2, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 14}
DiagrammeR::mermaid("
  graph LR
    X(START) --> A[<center>1.<br/>Write<br/>Markdown<br/>document</center>] 
    A        --> B[<center>2.<br/>Send Markdown<br/>document to<br/>GitHub</center>]
    B        --> C[<center>3.<br/>GitHub sends<br/>Markdown<br/>document to<br/>Netlify</center>]
    C        --> D[<center>4.<br/>Netlify converts<br/>Markdown and<br/>publishes HTML<br/>online</center>]
    D        --> Y(END)
  ", 
  height = 200)
```

---

# Our workflow for publishing Markdown to online newspaper

* You will notice that in our workflow, all we have to do are **Step 1** and **Step 2**. 

* **Step 3** and **Step 4** are all done automatically for us.

* The online tools that help us are **GitHub** and **Netlify**

.pull-left[
<p align="center"><img src="https://avatars1.githubusercontent.com/u/583231?s=400&v=4" width="250px" /></p>
]

.pull-right[
<p align="center"><img src="https://www.netlify.com/img/press/logos/full-logo-light.svg" width="250px" /></p>
]

---
